A GIS based workflow for Ecosystem Condition Accounting - an example using spatially biased indicators

### 2024-01-11 manuscript.Rmd
write methods

In this study we focused on open mire ecosystems in Norway.
For this ecosystem we have an ecosystem delineation map produced using a  
a deep learning model which was trained on field verified ground truth data and and satellite imagery. 
This model had a XX% precision when tested against independent field data.

The reference state defining ecosystems in optimal or pristine condition is defined as one with little or no human influence, with a climate as in the period 1961-1990 and a native species similar as today (no mammoths allowed).

We then identified two _concepts_ that define open mire ecosystems in optimal condition:

- Native species dominate
- No physical damage caused by human activities

@@

1. Alien plant cover
1. 7SE
1. 7TK
1. PR..
1. PR..

The data set from a standardised field survey of nature types.
Each locality is scored on a range of variables relevant for describing the state and quality of nature.
The surveys are comissioned with the goal of producing rel spatially

>>>>

In this study we focused on open mire ecosystems in Norway.
For this ecosystem we have an ecosystem delineation map produced using remotely sensed data and  
a deep learning model.
This model had a XX% precision when tested against independent field data.

The reference state defining ecosystems in optimal or pristine condition is defined as one with little or no human influence, with a climate as in the period 1961-1990 and a native species similar as today (i.ei no mammoths allowed).

We then identified two _ecosystem condition characteristics_ that, along with many other characteristics that we do not specify here, define the typical behavior of open mire ecosystems in the reference condition:

- Species composition
- Vegetation intactness

@@

1. 7FK (prevalence of alien species)
1. 7SE (tracks from large vehicles)
1. 7TK (human caused abration or abration-caused erosion)
1. PRTK (same as 7TK, but recorded at a higher resolution)
1. PRSL (same as 7SE, but recorded at a higher resolution)

Varaibles 1-3 are defined in Halvorsen and Bratli 2019.
Variables 4 and 5 are defined in ...

The data set from a standardised field survey of nature types in Norway (REF).
Each locality is scored on a range of variables relevant for describing the state and quality of nature.
The surveys are comissioned with the goal of producing data relevant for immediate land-use decisions, and is therefore
spatially biased, typically towards areas with high human impact or expected impact.
